Is malaria control profitable? Return on investment of privately-managed residential fumigations at a large sugarcane processing facility in Southern Mozambique

### 2018-04-12 inst/rmd/00_title_page.Rmd
major improvements

\noindent\fbox{%
    \parbox{\textwidth}{%
        \subsection*{Research Highlights}
        \begin{itemize}
          \item Large, individual-level worker absenteeism data from malaria endemic zone
          \item Quantifies effect of indoor residual spraying on absenteeism
          \item Estimates cost-effectiveness of malaria control from investment standpoint
          \item Results suggest that private sector could play a significant role in malaria elimination
        \end{itemize}
        \vspace{2mm}
    }%
}

>>>>

\noindent\fbox{%
    \parbox{\textwidth}{%
        \subsection*{Research Highlights}
        \begin{itemize}
          \item This paper analyzes large, individual-level worker absenteeism data from malaria endemic zone. 
          \item We quantify the effect of indoor residual spraying on absenteeism and clinical malaria. 
          \item We estimate cost-effectiveness of malaria control from an investment standpoint. 
          \item Results show ledger profitability, suggesting that the private sector could play a significant role in malaria elimination.  
        \end{itemize}
        \vspace{2mm}
    }%
}

### 2018-04-12 inst/rmd/01_introduction.Rmd
major improvements

Sugar has been systematically cultivated in Mozambique since the late 1800s, but was not exported at a large scale until the 1950s. The Incomati Estates company, a small sugarcane processing facility started by a Scotsman on the banks of the Incomati River in 1913, was the first firm to export sugar from Mozambique. Following its purchase by international investors in the 1950s, it (along with the rest of the industry) expanded significantly. In the late 1960s, a Portuguese family opened the Maragra Açúcar company, while a group of foreign investors started the nearby Marracuene Agrícola Açucareira mill. By the early 1970s, sugar grew to account for greater than 10% of Mozambique's national exports. Nationalized following independence in 1977, the industry's production levels fell from 320,000 annual tons to fewer than 15,000 in 1992. After the end of the civil war, foreign investment revived the sugar industry, and by 2011 production had surpassed its 1972 peak.

The mill of the Maragra Açucar SA (a subsidary of the Illovo sugar company, henceforth referred to as "Maragra") was nationalized in the 1970s (like all other mills), went through a period of low production, and then fell completely out of use by 1984. It re-opened in private hands in 1992, and was renovated by a group of international investors in 1998. Today, Maragra accounts for roughly one quarter of Mozambique's overall sugar production (second only to the nearby Xinavane mill run by the Hulett Sugar Tongaat company) [@sutton]. With a favorably close location to the port of Maputo, ample land, approximately 5,000 employees (of which three quarters are seasonal), and a mill with the capacity to process not only all the sugarcane grown on Maragra's land, but also the cane of the many nearby smallholders [@OLaughlin2016], Maragra has so far been able to weather the 2016 Mozambican crisis and concurrent collapse in global sugar prices.

>>>>

Sugar has been systematically cultivated in Mozambique since the late 1800s. The Incomati Estates company, a small sugarcane processing facility started by a Scotsman on the banks of the Incomati River in 1913, was the first firm to export sugar from Mozambique. Following its purchase by international investors in the 1950s, it (along with the rest of the industry) expanded significantly, exporting to both Europe and the United States. In the late 1960s, a Portuguese family opened the Maragra Açúcar company, while a group of foreign investors started the nearby Marracuene Agrícola Açucareira mill. By the early 1970s, sugar grew to account for greater than 10% of Mozambique's national exports. Nationalized following independence in 1977, the industry's production levels fell from 320,000 annual tons to fewer than 15,000 by 1992. After the end of the civil war, foreign investment revived the sugar industry, and by 2011 production had surpassed its 1972 peak.

The mill of the Maragra Açucar SA (a subsidary of the Illovo sugar company, henceforth referred to as "Maragra") was nationalized in the 1970s (like all other Mozambican mills), went through a period of low production, and then fell completely out of use by 1984. It re-opened in private hands in 1992, and was renovated by a group of international investors in 1998. Today, Maragra accounts for roughly one quarter of Mozambique's overall sugar production (second only to the nearby Xinavane mill run by the Hulett Sugar Tongaat company) [@sutton]. With a favorably close location to the port of Maputo, ample land, approximately 5,000 employees (of which three quarters are seasonal), and a mill with the capacity to process not only all the sugarcane grown on Maragra's land, but also the cane of the many nearby smallholders [@OLaughlin2016], Maragra has so far been able to weather the 2016 Mozambican crisis and concurrent collapse in global sugar prices.

Maragra is located in the district of Manhiça, a semi-rural area in Southern Mozambique

```{r, fig.width = 6, fig.align='center', fig.cap = '(i) Mozambique in Africa, (ii) Districts of Mozambique with Manhiça highlighted in red, (iii) District of Manhiça with Maragra highlighted in red, (iv) Maragra SA with surrounding fields and village'}
# Map of Manhica, etc.
# Libraries
library(tidyverse)
library(raster)
library(tidyr)
library(ggplot2)
library(RColorBrewer)
library(broom)
library(ggthemes)

# Get each countries shapefile
countries <- c('Mozambique')
iso3s <- c('MOZ')
for(i in 1:length(countries)){
  message('Fetching data for ', countries[i])
  x <- getData(name = 'GADM', level = 2, country = iso3s[i])
  assign(tolower(countries[i]),
         x,
         envir = .GlobalEnv)
}

# Define which districts are "special" -------------
specials <- 'Manhiça'

# Mozambique
mozambique@data$special <- FALSE
mozambique@data$special[mozambique@data$NAME_2 %in% specials] <- TRUE

# Combine all data into a "long" / "tidy" format
make_long <- function(x, region = "NAME_2"){
  shp_df <- broom::tidy(x, region = region)
  return(shp_df)
}
mozambique_long <- make_long(mozambique) %>% mutate(country = 'Mozambique')
combined <- mozambique_long
combined$special <- combined$id %in% specials
# combined$special[!combined$special] <- NA
# Get a map of africa to use as a background
# from the cism package!
africa <- cism::africa
africa_long <- make_long(africa, region = 'COUNTRY')
africa_long$special <- africa_long$id %in% countries

g1 <-
  ggplot() +
  geom_polygon(data = africa_long,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = grey(0.6),
               alpha = 1,
               color = 'white',
               lwd = 0.3) +
  geom_polygon(data = combined,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = grey(0.3)) +
  geom_polygon(data = combined %>% filter(!is.na(special) & special),
               aes(x = long,
                   y = lat,
                   group = group,
                   fill = special)) +
  scale_fill_manual(name = '',
                    values = c('darkorange'),
                    na.value = NA) +
  coord_cartesian() +
  ggthemes::theme_map() +
  theme(legend.position = 'none') +
  # redraw country lines
  geom_polygon(data = africa_long,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = NA,
               alpha = 1,
               color = 'white',
               lwd = 0.3) + coord_map() +
  labs(title = 'i.')
country_map <- function(the_country = 'Gabon'){
  ggplot(data = combined %>% filter(country == the_country),
         aes(x = long,
             y = lat,
             group = group,
             fill = special)) +
    geom_polygon(#alpha = 0.8,
                 lwd = 0.3,
                 color = grey(0.6)) +
    theme_map() +
    coord_map() + 
    scale_fill_manual(name = '', values = c('darkgrey', 'darkred')) +
    theme(legend.position = 'none')
}
g2 <- country_map('Mozambique') +
  labs(title = 'ii.')

mar <- data.frame(lat = -25.4498802, long = 32.777661)
man3_fortified <- cism::man3_fortified
g3 <- ggplot(data = man3_fortified,
             aes(x = long,
                 y = lat)) +
  geom_polygon(aes(group = group),
               # alpha = 0.8,
                 lwd = 0.3,
                 color = grey(0.6)) +
  geom_point(data = mar,
             aes(x = long,
                 y = lat),
             color = 'red') +
  geom_point(data = mar,
             aes(x = long,
                 y = lat),
             color = 'red',
             size = 4, 
             pch = 1) +
  geom_point(data = mar,
             aes(x = long,
                 y = lat),
             color = 'red',
             size = 6, 
             pch = 1) +
  geom_point(data = mar,
             aes(x = long,
                 y = lat),
             color = 'red',
             size = 9, 
             pch = 1) +
    theme_map() +
    coord_map() + 
    theme(legend.position = 'none') +
  labs(title = 'iii')

library(ggmap)
# if('.hdf.RData' %in% dir()){
#   load('.hdf.RData')
# } else {
  hdf <- ggmap::get_map(location = c(lon = mar$long, lat = mar$lat), maptype = 'satellite', zoom = 14)
#   save(hdf, file = '.hdf.RData')
# }

g4 <- ggmap::ggmap(hdf) +
  theme_map() +
  labs(title = 'iv')

Rmisc::multiplot(g1, g2, g3, g4, cols = 2)
```

### 2018-04-12 inst/rmd/03_results.Rmd
major improvements

Given the likelihood that clinical data does not fully capture all malaria cases, we do not quantify the costs of malaria infection to the company. Rather, we first estimate the reduction in absenteeism attributible to IRS, and then quantify the savings associated with prevented absences. Additionally, we calculate the clinical savings of IRS by first estimating the share of absences which are associated with an episode of clinical malaria, and then applying the clinical cost per case to the equivalent share of prevented absences. We intentionally ignore the savings accrued by the public health system, as well as the likely utility gains in secondary realms such as school absenteeism, producitivity, etc.

>>>>

Given the likelihood that clinical data does not fully capture all malaria cases (and most likely captures only a small fraction of actual infections, given the high rates of acumulated adult immunity [Mayor2007]), we do not quantify the costs of malaria infection to the company. Rather, we first estimate the reduction in absenteeism attributible to IRS, and then quantify the savings associated with prevented absences. Additionally, we calculate the clinical savings of IRS by first estimating the share of absences which are associated with an episode of clinical malaria, and then applying the clinical cost per case to the equivalent share of prevented absences. We intentionally ignore the savings accrued by the public health system, as well as the likely utility gains in secondary realms such as school absenteeism, producitivity, etc.

### 2018-04-12 inst/rmd/paper.Rmd
major improvements

---
title: Return on investment of private sector malaria control at a large sugar
  facility in Southern Mozambique
date: ''
output: 
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
    includes:
      in_header: preamble.sty
fig_width: 4
fig_height: 2.6
bibliography: bibliography.bib
csl: journal-of-health-economics.csl
---

>>>>

---
title: Is malaria control profitable? Return on investment of privately-managed residential fumigations at a large sugarcane processing facility in Southern Mozambique
date: ''
output: 
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
    includes:
      in_header: preamble.sty
fig_width: 4
fig_height: 2.6
bibliography: bibliography.bib
csl: journal-of-health-economics.csl
---

### 2018-04-12 inst/rmd/paper.tex
major improvements

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Return on investment of private sector malaria control at a large sugar facility in Southern Mozambique},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{Return on investment of private sector malaria control at a large sugar
facility in Southern Mozambique}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

@@

Sugar has been systematically cultivated in Mozambique since the late
1800s, but was not exported at a large scale until the 1950s. The
Incomati Estates company, a small sugarcane processing facility started
by a Scotsman on the banks of the Incomati River in 1913, was the first
firm to export sugar from Mozambique. Following its purchase by
international investors in the 1950s, it (along with the rest of the
industry) expanded significantly. In the late 1960s, a Portuguese family
opened the Maragra Açúcar company, while a group of foreign investors
started the nearby Marracuene Agrícola Açucareira mill. By the early
1970s, sugar grew to account for greater than 10\% of Mozambique's
national exports. Nationalized following independence in 1977, the
industry's production levels fell from 320,000 annual tons to fewer than
15,000 in 1992. After the end of the civil war, foreign investment
revived the sugar industry, and by 2011 production had surpassed its
1972 peak.

The mill of the Maragra Açucar SA (a subsidary of the Illovo sugar
company, henceforth referred to as ``Maragra'') was nationalized in the
1970s (like all other mills), went through a period of low production,
and then fell completely out of use by 1984. It re-opened in private
hands in 1992, and was renovated by a group of international investors
in 1998. Today, Maragra accounts for roughly one quarter of Mozambique's
overall sugar production (second only to the nearby Xinavane mill run by
the Hulett Sugar Tongaat company) (Sutton, 2015). With a favorably close
location to the port of Maputo, ample land, approximately 5,000
employees (of which three quarters are seasonal), and a mill with the
capacity to process not only all the sugarcane grown on Maragra's land,
but also the cane of nearby smallholders, Maragra has so far been able
to weather the 2016 Mozambican crisis and concurrent collapse in global
sugar prices.

\begin{itemize}
\tightlist
\item
  Details on Maragra: .
\end{itemize}

-Xinavane (O'Laughlin, 2016)

@@

\subsection{Data collection}\label{data-collection}

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-13-1.pdf}
\caption{Clinical malaria (district of Manhiça), all-cause absenteeism
among Maragra workers, sick absenteeism among Maragra workers, estimated
rainfall, positive cases at company clinic, and test positivity rate at
company clinic}
\end{figure}

@@

Given the likelihood that clinical data does not fully capture all
malaria cases, we do not quantify the costs of malaria infection to the
company. Rather, we first estimate the reduction in absenteeism
attributible to IRS, and then quantify the savings associated with
prevented absences. Additionally, we calculate the clinical savings of
IRS by first estimating the share of absences which are associated with
an episode of clinical malaria, and then applying the clinical cost per
case to the equivalent share of prevented absences. We intentionally
ignore the savings accrued by the public health system, as well as the
likely utility gains in secondary realms such as school absenteeism,
producitivity, etc.

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-16-1.pdf}
\caption{Estimated effect of IRS on absenteeism by season}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-17}Models with worker fixed effects}
\centering
\begin{tabular}[t]{ll}
\toprule
Term & Estimate\\
\midrule
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent field worker}}\\
\hspace{1em}Off site & 9.142 (P<0.001)\\
\hspace{1em}On site & 11.424 (P<0.001)\\
\hspace{1em}Malaria season & 3.424 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & 3.831 (P<0.001)\\
\hspace{1em}Months since IRS: 02-04 & 4.199 (P<0.001)\\
\hspace{1em}Months since IRS: 05-09 & -3.194 (P<0.001)\\
\hspace{1em}Months since IRS: 10+ & -5.794 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -4.534 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & -8.392 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -3.85 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 10+ & 4.504 (P=0.002)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent not field worker}}\\
\hspace{1em}Off site & 10.862 (P<0.001)\\
\hspace{1em}On site & 9.555 (P<0.001)\\
\hspace{1em}Malaria season & 2.077 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & -2.083 (P<0.001)\\
\hspace{1em}Months since IRS: 02-04 & 3.904 (P<0.001)\\
\hspace{1em}Months since IRS: 05-09 & -0.834 (P=0.084)\\
\hspace{1em}Months since IRS: 10+ & -0.268 (P=0.742)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 2.735 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & -5.768 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -2.441 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 10+ & 4.497 (P<0.001)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary field worker}}\\
\hspace{1em}Off site & 0.985 (P<0.001)\\
\hspace{1em}On site & 1.078 (P<0.001)\\
\hspace{1em}Malaria season & -0.017 (P=0.461)\\
\hspace{1em}Months since IRS: 01 & -0.4 (P<0.001)\\
\hspace{1em}Months since IRS: 02-04 & -0.547 (P<0.001)\\
\hspace{1em}Months since IRS: 05-09 & -0.554 (P<0.001)\\
\hspace{1em}Months since IRS: 10+ & -0.992 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -0.092 (P=0.62)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & 0.172 (P=0.256)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & 0.062 (P=0.657)\\
\hspace{1em}Malaria season:Months since IRS: 10+ & 0.068 (P=0.771)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary not field worker}}\\
\hspace{1em}Off site & 4.136 (P<0.001)\\
\hspace{1em}On site & 3.834 (P<0.001)\\
\hspace{1em}Malaria season & -0.292 (P=0.16)\\
\hspace{1em}Months since IRS: 01 & -1.456 (P=0.389)\\
\hspace{1em}Months since IRS: 02-04 & 0.608 (P=0.574)\\
\hspace{1em}Months since IRS: 05-09 & -0.869 (P=0.405)\\
\hspace{1em}Months since IRS: 10+ & 10.583 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 6.045 (P=0.002)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & 0.604 (P=0.667)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -1.482 (P=0.284)\\
\hspace{1em}Malaria season:Months since IRS: 10+ & -10.636 (P<0.001)\\
\bottomrule
\end{tabular}
\end{table}

@@

\hypertarget{ref-sutton}{}
Sutton, J., 2015. Mapa empresarial de moçambique.

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Is malaria control profitable? Return on investment of privately-managed residential fumigations at a large sugarcane processing facility in Southern Mozambique},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{Is malaria control profitable? Return on investment of privately-managed
residential fumigations at a large sugarcane processing facility in
Southern Mozambique}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

@@

Sugar has been systematically cultivated in Mozambique since the late
1800s. The Incomati Estates company, a small sugarcane processing
facility started by a Scotsman on the banks of the Incomati River in
1913, was the first firm to export sugar from Mozambique. Following its
purchase by international investors in the 1950s, it (along with the
rest of the industry) expanded significantly, exporting to both Europe
and the United States. In the late 1960s, a Portuguese family opened the
Maragra Açúcar company, while a group of foreign investors started the
nearby Marracuene Agrícola Açucareira mill. By the early 1970s, sugar
grew to account for greater than 10\% of Mozambique's national exports.
Nationalized following independence in 1977, the industry's production
levels fell from 320,000 annual tons to fewer than 15,000 by 1992. After
the end of the civil war, foreign investment revived the sugar industry,
and by 2011 production had surpassed its 1972 peak.

The mill of the Maragra Açucar SA (a subsidary of the Illovo sugar
company, henceforth referred to as ``Maragra'') was nationalized in the
1970s (like all other Mozambican mills), went through a period of low
production, and then fell completely out of use by 1984. It re-opened in
private hands in 1992, and was renovated by a group of international
investors in 1998. Today, Maragra accounts for roughly one quarter of
Mozambique's overall sugar production (second only to the nearby
Xinavane mill run by the Hulett Sugar Tongaat company) (Sutton, 2014).
With a favorably close location to the port of Maputo, ample land,
approximately 5,000 employees (of which three quarters are seasonal),
and a mill with the capacity to process not only all the sugarcane grown
on Maragra's land, but also the cane of the many nearby smallholders
(O'Laughlin, 2016), Maragra has so far been able to weather the 2016
Mozambican crisis and concurrent collapse in global sugar prices.

Maragra is located in the district of Manhiça, a semi-rural area in
Southern Mozambique

\begin{figure}[H]

{\centering \includegraphics{figures/unnamed-chunk-13-1}

}

\caption{(i) Mozambique in Africa, (ii) Districts of Mozambique with Manhiça highlighted in red, (iii) District of Manhiça with Maragra highlighted in red, (iv) Maragra SA with surrounding fields and village}\label{fig:unnamed-chunk-13}
\end{figure}

@@

\subsection{Data}\label{data}

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-14-1.pdf}
\caption{Clinical malaria (district of Manhiça), all-cause absenteeism
among Maragra workers, sick absenteeism among Maragra workers, estimated
rainfall, positive cases at company clinic, and test positivity rate at
company clinic}
\end{figure}

@@

Given the likelihood that clinical data does not fully capture all
malaria cases (and most likely captures only a small fraction of actual
infections, given the high rates of acumulated adult immunity
{[}Mayor2007{]}), we do not quantify the costs of malaria infection to
the company. Rather, we first estimate the reduction in absenteeism
attributible to IRS, and then quantify the savings associated with
prevented absences. Additionally, we calculate the clinical savings of
IRS by first estimating the share of absences which are associated with
an episode of clinical malaria, and then applying the clinical cost per
case to the equivalent share of prevented absences. We intentionally
ignore the savings accrued by the public health system, as well as the
likely utility gains in secondary realms such as school absenteeism,
producitivity, etc.

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-17-1.pdf}
\caption{Estimated effect of IRS on absenteeism by season}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-18}Models with worker fixed effects}
\centering
\begin{tabular}[t]{ll}
\toprule
Term & Estimate\\
\midrule
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent field worker}}\\
\hspace{1em}Off site & 9.142 (P<0.001)\\
\hspace{1em}On site & 11.424 (P<0.001)\\
\hspace{1em}Malaria season & 3.424 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & 3.831 (P<0.001)\\
\hspace{1em}Months since IRS: 02-04 & 4.199 (P<0.001)\\
\hspace{1em}Months since IRS: 05-09 & -3.194 (P<0.001)\\
\hspace{1em}Months since IRS: 10+ & -5.794 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -4.534 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & -8.392 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -3.85 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 10+ & 4.504 (P=0.002)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent not field worker}}\\
\hspace{1em}Off site & 10.862 (P<0.001)\\
\hspace{1em}On site & 9.555 (P<0.001)\\
\hspace{1em}Malaria season & 2.077 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & -2.083 (P<0.001)\\
\hspace{1em}Months since IRS: 02-04 & 3.904 (P<0.001)\\
\hspace{1em}Months since IRS: 05-09 & -0.834 (P=0.084)\\
\hspace{1em}Months since IRS: 10+ & -0.268 (P=0.742)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 2.735 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & -5.768 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -2.441 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 10+ & 4.497 (P<0.001)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary field worker}}\\
\hspace{1em}Off site & 0.985 (P<0.001)\\
\hspace{1em}On site & 1.078 (P<0.001)\\
\hspace{1em}Malaria season & -0.017 (P=0.461)\\
\hspace{1em}Months since IRS: 01 & -0.4 (P<0.001)\\
\hspace{1em}Months since IRS: 02-04 & -0.547 (P<0.001)\\
\hspace{1em}Months since IRS: 05-09 & -0.554 (P<0.001)\\
\hspace{1em}Months since IRS: 10+ & -0.992 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -0.092 (P=0.62)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & 0.172 (P=0.256)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & 0.062 (P=0.657)\\
\hspace{1em}Malaria season:Months since IRS: 10+ & 0.068 (P=0.771)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary not field worker}}\\
\hspace{1em}Off site & 4.136 (P<0.001)\\
\hspace{1em}On site & 3.834 (P<0.001)\\
\hspace{1em}Malaria season & -0.292 (P=0.16)\\
\hspace{1em}Months since IRS: 01 & -1.456 (P=0.389)\\
\hspace{1em}Months since IRS: 02-04 & 0.608 (P=0.574)\\
\hspace{1em}Months since IRS: 05-09 & -0.869 (P=0.405)\\
\hspace{1em}Months since IRS: 10+ & 10.583 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 6.045 (P=0.002)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & 0.604 (P=0.667)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -1.482 (P=0.284)\\
\hspace{1em}Malaria season:Months since IRS: 10+ & -10.636 (P<0.001)\\
\bottomrule
\end{tabular}
\end{table}

@@

\hypertarget{ref-sutton}{}
Sutton, J., 2014. Mapa empresarial de moçambique.
